Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-09 Paper/paper.tex
Finished Testing Survey edits

\section{Browser and UI Testing}
Web applications, for the most part, require user input in order to be useful. The way the user interacts is through the outward facing web pages. Testing of a web application would be incomplete without testings the interactions and elements of these web pages. It's important that the inner workings are running the right code and producing the right answer, but it's almost just as important that the parameters get passed correctly and from the right places on the web pages. Also, it is important that navigation work as expected or a user will become frustrated and lose interest in the application.

@@

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser driver. It is one of the only automated browser drivers; in all of our searching, we did not find a single other browser automation tool, all other frameworks were built on top of Selenium. A developer can write code that will cause Selenium to drive a browser's input and assert expectations. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

Generally, all browser testing tools will be using Selenium behind the scenes and doing the housekeeping automatically. This is the case for the web testing tools that will follow this description.

Selenium has support for running a number of different browsers. Out of the box it comes with support for Firefox but getting Chrome and Safari running takes minimal effort.

@@

\subsection{Nightwatchjs}
Nightwatch\cite{NightwatchJS} is a JavaScript testing library that wraps Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to time constraints and the added complexity of running headless browsers.

@@

\begin{lstlisting}
// Zombie.js website's example code
var Browser = require("zombie");
var assert = require("assert");

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what it looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

@@

Jenkins comes bare-boned but is highly customizable and has a wide array of plugins. The plugins available integrate Jenkins with various services, integrate Jenkins with source control systems, and even just change the look of the Jenkins page or how it behaves. As an example, Jenkins can integrate with GitHub to run builds and tests when changes are pushed to a branch.

@@

Travis comes with internal support for eleven different languages including Node.JS, Ruby, Java, and Python. Travis has incredibly thorough documentation and a wealth of built-in services to work with projects if needed. Theses services include databases, notifications, deployment options, and GUI/Headless browsers. Travis supports all of the most popular databases: MySql, PostgreSql, MongoDB, CouchDB, and a myriad of others. It offers a number of notification options ranging from Email to IRC to HipChat (a chat service from Atlassian). Travis also offers deployment to just about every sort of provider there is, from Heroku to AWS S3 to RubyGems and also provides the ability to create custom web hooks to deploy to a provider not supported natively.

If at any point the project requires something that Travis does not support natively, Travis gives the permissions necessary to install any sort of libraries or services that can be installed with apt-get on an Ubuntu machine.

@@

In order to get access to private repositories, Travis offers several pricing plans, the cheapest of which is \$129\cite{TravisPricing} for their ``Startup'' plan. That's a bit steep, but it does offer unlimited private repositories, unlimited collaborators, and two concurrent jobs.

From what we gathered, Travis appears to be targeted at companies, not individual developers. Travis requires developers to host their projects on GitHub and only supports one process running at a time. However, Travis is incredibly easy to set up, does not require it's own server, comes with impressive built-in features, and works wonderfully with open-source repositories on GitHub.

@@

Semaphore supports most databases and has a number of testing frameworks built-in. Once again any missing libraries or dependencies can be installed using apt-get. It would appear that deployment support is only available for Ruby projects.

@@

Semaphore is still ruby-centric and requires a subscription. As our goal is to find a framework that is free for open-source projects, Semaphore was out automatically. It is included here because it's well-known and fairly established, especially in the ruby community.

@@

\subsection{Manual Continuous Integration}
Most of what these CI frameworks accomplish can be done by hand with enough script writing. Continuous Integration tools are notified of updates by scripts that run after a commit is pushed. With the Continuous Integration scripts above, the post commit scripts are written without the knowledge of the developer. There is, however, no reason that a developer cannot hook into those scripts themselves.

Manual CI is incredibly similar to Jenkins in that its only limitations are the libraries and hardware that it's run on.

@@

Finally, manual CI uses a developer's system, rendering it unusable to the developer, particularly during the UI testing phase. The developer must accept a productivity hit every time they commit to their repository.

@@

Grunt is widely supported and has all kinds of built-in or installable plugins that make writing common tasks nearly trivial. As an example, a few built-in grunt tasks that we use include: \lstinline{jshint} for linting, \lstinline{uglify} for code minimization, and \lstinline{watch} for automatically re-running tests when certain files change. Each of those plugins requires very little configuration and they're ready to be used.

>>>>

\section{Browser and UI Testing}
Web applications, for the most part, require user input in order to be useful. The way the user interacts is through the outward facing web pages. Testing of a web application would be incomplete without testing the interactions and elements of these web pages. It's important that the inner workings are running the right code and producing the right answer, but it's almost just as important that the parameters get passed correctly and from the right places on the web pages. Also, it is important that navigation work as expected or a user will become frustrated and lose interest in the application.

@@

\subsection{Selenium}
Selenium\cite{Selenium} is an automated browser driver. It is one of the only automated browser drivers; in all of our searching, we did not find a single other browser automation tool, all other frameworks were built on top of Selenium. A developer can write code that will cause Selenium to drive a browser. On its own Selenium has very minimal testing usage. It lacks a test reporting mechanism and only offers output in two forms: 1) No output at all, a browser window will open, input will be generated, and the window will close, or 2) the browser will exit with a cryptic error printed to the console. It is up to the developer to include print statements as to what is happening at any given time, what test is being run, and what the results are.

Generally, all browser testing tools will be using Selenium behind the scenes and doing the housekeeping automatically. This is the case for the web testing tool that will follow this description.

Selenium has support for running a number of different browsers. Out of the box it comes with support for Firefox but getting Chrome, Safari, and Internet Explorer running takes minimal effort.

@@

\subsection{Nightwatchjs}
Nightwatch\cite{NightwatchJS} is a JavaScript testing library built on top of Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

\subsection{Headless Browsers}
In an attempt to speed up UI testing, which is notoriously slow, there have been efforts to create ``headless'' browsers which behave like normal browsers except that there's no display element. They emulate the DOM and skip the display phase. We opted to stick with visual browsers due to the added complexity of running headless browsers.

@@

The following is an excerpt from ZombieJS's examples:
\begin{lstlisting}
// Zombie.js website's example code
var Browser = require("zombie");
var assert = require("assert");

@@

Jenkins is a series of web pages that are set up to run on a given server. This is what Jenkins looks like:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{jenkins.png}

@@

Jenkins comes without many features but is highly customizable and has a wide array of plugins. The plugins integrate Jenkins with various services, integrate Jenkins with source control systems, and even just change the look of the Jenkins page or how it behaves. As an example, Jenkins can integrate with GitHub to run builds and tests when changes are pushed to a branch.

@@

Travis comes with internal support for eleven different languages including Node.JS, Ruby, Java, and Python. Travis has incredibly thorough documentation and a wealth of built-in services to work with projects. Theses services include databases, notifications, deployment options, and GUI/Headless browsers. Travis supports all of the most popular databases: MySQL, PostgreSQL, MongoDB, CouchDB, and a myriad of others. It offers a number of notification options ranging from Email to IRC to HipChat (a chat service from Atlassian). Travis also offers deployment options, from Heroku to AWS S3 to RubyGems and also provides the ability to create custom web hooks to deploy to a provider not supported natively.

If at any point the project requires something that Travis does not support natively, Travis gives the developer permissions necessary to install any sort of libraries or services that can be installed with apt-get on an Ubuntu machine.

@@

In order to get access to private repositories, Travis offers several pricing plans, the cheapest of which is \$129 for their ``Startup'' plan\cite{TravisPricing}. That's a bit steep, but it does offer unlimited private repositories, unlimited collaborators, and two concurrent jobs.

From what we gathered, Travis appears to be targeted at companies, not individual developers. Travis requires developers to host their projects on GitHub and only supports one process running at a time. However, Travis is incredibly easy to set up, does not require its own server, comes with impressive built-in features, and works wonderfully with open-source repositories on GitHub.

@@

Semaphore supports most databases and has a number of testing frameworks built-in. Once again any missing libraries or dependencies can be installed using apt-get. Deployment support is only available for Ruby projects as of this writing.

@@

Semaphore is still ruby-centric and requires a subscription. As our goal is to find a framework that is free for open-source projects, Semaphore was out automatically. It is included here because it is well-known and fairly established, especially in the ruby community.

@@

\subsection{Manual Continuous Integration}
Most of what these CI frameworks accomplish can be done by hand with enough script writing. Continuous Integration tools are notified of updates by scripts that run after a commit is pushed. The Continuous Integration tools above write these ``post-commit'' scripts without the knowledge of the developer. There is, however, no reason that a developer cannot write those scripts themselves.

Manual CI is incredibly similar to Jenkins in that its only limitations are the libraries and hardware that the scripts are run on.

@@

Finally, Manual CI uses a developer's system, rendering it unusable to the developer, particularly during the UI testing phase. The developer must accept a productivity hit every time they commit to their repository.

@@

Grunt is widely supported and has all kinds of built-in or installable plugins that make writing common tasks nearly trivial. As an example, a few built-in grunt tasks that we use include: \lstinline{jshint} for linting, \lstinline{uglify} for code minimization, and \lstinline{watch} for automatically re-running tests when certain files change. Each of those plugins requires very little configuration before they are ready to be used.
